---
title: "Branch Selection Rates & Graphs"
output: html_notebook
---


```{r}
##Behavioral Graph selection rates by condition
library(ggplot2)
library(Rmisc)
library(reshape2)
library(ggsignif)

branchsr <- read.csv('BranchSRs_022122.csv')
branchsr$ID <- 1:nrow(branchsr)

branchsrlong <- melt(branchsr, id.vars='ID', variable.name='condition', value.name='selectionrate')
SRsumm <- summarySE(data=branchsrlong, measurevar='selectionrate', groupvars='condition')

#create graph
p_ac <- ggplot(data = SRsumm,aes(y=selectionrate,x=condition)) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black")) + 
  geom_bar(stat = 'identity', color = 'black', fill='steelblue', position = position_dodge(.9)) +
  geom_errorbar(aes(ymin = selectionrate-se, ymax = selectionrate+se,width = .3),position=position_dodge(.9)) +
 geom_text(aes(x = condition, y = selectionrate, label = round(selectionrate, digits=2)), position = position_stack(vjust = .5), size = 4)+
  ggtitle('Selection Rates by Condition') + 
  theme(plot.title = element_text(hjust = 0.5, size=17),
        axis.text.x=element_text(size=15),
        axis.text.y=element_text(size=15), axis.title.x=element_text(size=15),
        axis.title.y=element_text(size=15)) +
  labs(fill=' ', x = ' Condition', y='Selection Rate') 
p_ac


controldelay <- t.test(branchsr$Control, branchsr$Delay, paired=T)
controlswitch <- t.test(branchsr$Control, branchsr$Switch, paired=T)
controldual <- t.test(branchsr$Control, branchsr$Dual, paired=T)
delayswitch <- t.test(branchsr$Delay, branchsr$Switch, paired=T)
delaydual <- t.test(branchsr$Delay, branchsr$Dual, paired=T)
switchdual <- t.test(branchsr$Switch, branchsr$Dual, paired=T)

p.vals <- c(controldelay$p.value, controlswitch$p.value, controldual$p.value, delayswitch$p.value, delaydual$p.value, switchdual$p.value)

p.adjust(p.vals, "bonferroni")
```
```{r}
library(ggplot2)
library(Rmisc)
library(reshape2)
library(ggsignif)

branchRT1 <- read.csv('BranchRTs_022122.csv')
branchRT1$Phase <- 'Selection'
branchRT2 <- read.csv('BranchRTs_Practice_022122.csv')
branchRT2$Phase <- 'Learning'

branchRTs <- rbind(branchRT1, branchRT2)

branchRTslong <- melt(branchRTs, id.vars=c('ID', 'Phase'), variable.name='condition', value.name='RT')
branchRTslong$RT <- branchRTslong$RT*1000
SRbranchRTs <- summarySE(data=branchRTslong, measurevar='RT', groupvars=c('condition', 'Phase'), na.rm=T)

aa <- ggplot(SRbranchRTs, aes(x=condition, y=RT)) +
  geom_line(aes(color=Phase, group=Phase)) +
  geom_point(aes(color=Phase, shape=Phase))+
  coord_cartesian (ylim=c(0,1400)) +
  geom_errorbar(aes(ymin = RT - se, ymax = RT + se, color=Phase, width=.5,), size=1.5) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
    panel.background = element_blank(), axis.line = element_line(colour = "black")) +
  ggtitle('Reaction Times by Condition') + 
  theme(plot.title = element_text(hjust = 0.5, size=17),
        axis.text.x=element_text(size=15),
        axis.text.y=element_text(size=15), axis.title.x=element_text(size=15),
        axis.title.y=element_text(size=15)) +
  labs(fill=' ', x = ' ', y='Reaction Times')
aa

```



```{r}
library(ggplot2)
library(Rmisc)
library(reshape2)
library(ggsignif)

branchAcc1 <- read.csv('BranchAcc_022122.csv')
branchAcc1$Phase <- 'Selection'
branchAcc2 <- read.csv('BranchAcc_Practice_022122.csv')
branchAcc2$Phase <- 'Learning'

branchAcc <- rbind(branchAcc1, branchAcc2)

branchAcclong <- melt(branchAcc, id.vars=c('ID', 'Phase'), variable.name='condition', value.name='Acc')
branchAcclong$Acc <- 1-branchAcclong$Acc
SRbranchAcc <- summarySE(data=branchAcclong, measurevar='Acc', groupvars=c('condition', 'Phase'), na.rm=T)

bb <- ggplot(SRbranchAcc, aes(x=condition, y=Acc)) +
  geom_line(aes(color=Phase, group=Phase)) +
  geom_point(aes(color=Phase, shape=Phase))+
  coord_cartesian (ylim=c(0,.3)) +
  geom_errorbar(aes(ymin = Acc - se, ymax = Acc + se, color=Phase, width=.5,), size=1.5) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
    panel.background = element_blank(), axis.line = element_line(colour = "black")) +
  ggtitle('Error Rate by Condition') + 
  theme(plot.title = element_text(hjust = 0.5, size=17),
        axis.text.x=element_text(size=15),
        axis.text.y=element_text(size=15), axis.title.x=element_text(size=15),
        axis.title.y=element_text(size=15)) +
  labs(fill=' ', x = ' ', y='Error Rate')
  

bb
```
Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

