---
title: "Hier Selection Rates & Graphs"
output: html_notebook
---
```{r}
##Behavioral Graph selection rates by condition
library(ggplot2)
library(Rmisc)
library(reshape2)
library(ggsignif)

hiersr <- read.csv('HierCostSRs_022122.csv')
hiersr$ID <- 1:nrow(hiersr)

hiersrlong <- melt(hiersr, id.vars='ID', variable.name='condition', value.name='selectionrate')
SRsumm <- summarySE(data=hiersrlong, measurevar='selectionrate', groupvars='condition')
SRsumm$condition <- c('R1', 'R2', 'R4', 'F1', 'F2', 'F4')
SRsumm$condition <- factor(SRsumm$condition, levels=c('R1', 'R2', 'R4', 'F1', 'F2', 'F4'))


#create graph
p_ac <- ggplot(data = SRsumm,aes(y=selectionrate,x=condition)) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black")) + 
  geom_bar(stat = 'identity', color = 'black', fill='steelblue', position = position_dodge(.9)) +
  geom_errorbar(aes(ymin = selectionrate-se, ymax = selectionrate+se,width = .3),position=position_dodge(.9)) +
 geom_text(aes(x = condition, y = selectionrate, label = round(selectionrate, digits=2)), position = position_stack(vjust = .5), size = 4)+
  ggtitle('Selection Rates by Condition') + 
  theme(plot.title = element_text(hjust = 0.5, size=17),
        axis.text.x=element_text(size=15),
        axis.text.y=element_text(size=15), axis.title.x=element_text(size=15),
        axis.title.y=element_text(size=15)) +
  labs(fill=' ', x = ' Condition', y='Selection Rate') + 
  annotate("text", x = 1.17, y = 1, label = "Abstraction Level 0") + 
  annotate("text", x = 3, y = .7, label = "Abstraction Level 1") +
  annotate("text", x=5.5, y=.4, label = "Abstraction Level 2") +
  geom_signif(comparisons=list(c("R2", "F1")), annotations=" ",
             y_position = .66, tip_length = 0, vjust=0.4) + 
  geom_signif(comparisons=list(c("F2", "F4")), annotations=" ",
             y_position = .36, tip_length = 0, vjust=0.4) 
p_ac
```


```{r}
library(ggplot2)
library(Rmisc)
library(reshape2)
library(ggsignif)

#hierratespair <- read.csv('HierPairwiseSelection.csv')
hierratespair$ID <- 1:nrow(hierratespair)

hierratespairlong <- melt(hierratespair, id.vars='ID', variable.name='pair', value.name='selectionrate')
SRhierratespair <- summarySE(data=hierratespairlong, measurevar='selectionrate', groupvars='pair', na.rm=T)

#create graph
p_ac_p <- ggplot(data = SRhierratespair,aes(y=selectionrate,x=pair)) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black")) + 
  geom_bar(stat = 'identity', color = 'black', fill='steelblue', position = position_dodge(.9)) +
  geom_errorbar(aes(ymin = selectionrate-se, ymax = selectionrate+se,width = .3),position=position_dodge(.9)) +
   geom_text(aes(x = pair, y = selectionrate, label = round(selectionrate, digits=2)), position = position_stack(vjust = .5), size = 4)+
  geom_hline(yintercept=.5, linetype="dashed", color = "red") +
  coord_cartesian(ylim=c(0,1)) + 
  ggtitle('Selected Pairwise Selection Rates') + 
  theme(plot.title = element_text(hjust = 0.5, size=17),
        axis.text.x=element_text(angle=45, hjust=1, size=12),
        axis.text.y=element_text(size=15), axis.title.x=element_text(size=15),
        axis.title.y=element_text(size=15)) +
  scale_x_discrete(labels = c('R vs F','R2 vs F1','R2 vs R4', 'F2 vs F4', 'R3 vs F3')) + 
  labs(fill=' ', x = ' ', y='Selection Rate')
p_ac_p
```




```{r}
library(ggplot2)
library(Rmisc)
library(reshape2)
library(ggsignif)

hierRT1 <- read.csv('HierCostRTs_022122.csv')
hierRT1$Phase <- 'Selection'
hierRT2 <- read.csv('HierCostRTs_Practice_022122.csv')
hierRT2$Phase <- 'Learning'

hierRTs <- rbind(hierRT1, hierRT2)

hierRTslong <- melt(hierRTs, id.vars=c('ID', 'Phase'), variable.name='condition', value.name='RT')
SRhierRTs <- summarySE(data=hierRTslong, measurevar='RT', groupvars=c('condition', 'Phase'), na.rm=T)
SRhierRTs$grp <- c('1', '1', '2', '2', '2', '2', '2', '2', '3', '3', '3', '3')
SRhierRTs$condition <- c('aR1', 'aR1', 'aR2', 'aR2', 'aR4', 'aR4', 'F1', 'F1', 'F2', 'F2', 'F4', 'F4')



aa <- ggplot(hierRTslong, aes(x=condition, y=RT, group=Phase)) +
  geom_boxplot() +
  coord_cartesian (ylim=c(0,1400)) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
    panel.background = element_blank(), axis.line = element_line(colour = "black")) +
  ggtitle('Reaction Times by Condition') + 
  theme(plot.title = element_text(hjust = 0.5, size=17),
        axis.text.x=element_text(size=15),
        axis.text.y=element_text(size=15), axis.title.x=element_text(size=15),
        axis.title.y=element_text(size=15)) +
  labs(fill=' ', x = ' ', y='Reaction Times')
#  scale_x_discrete(labels = c('R1','R2','R4', 'F1', 'F2', 'F4')) + 
#  annotate("text", x = 1.4, y = 550, size=4.5, label = "Abstraction Level 0") + 
#  annotate("text", x = 3, y = 1100, size=4.5, label = "Abstraction Level 1") +
#  annotate("text", x= 5.5, y=800, size=4.5, label = "Abstraction Level 2")
  
aa
```



```{r}
library(ggplot2)
library(Rmisc)
library(reshape2)
library(ggsignif)

hierAcc1 <- read.csv('HierCostAcc_022122.csv')
hierAcc1$Phase <- 'Selection'
hierAcc2 <- read.csv('HierCostAcc_Practice_022122.csv')
hierAcc2$Phase <- 'Learning'

hierAcc <- rbind(hierAcc1, hierAcc2)

hierAcclong <- melt(hierAcc, id.vars=c('ID', 'Phase'), variable.name='condition', value.name='Acc')
hierAcclong$Acc <- 1-hierAcclong$Acc
SRhierAcc <- summarySE(data=hierAcclong, measurevar='Acc', groupvars=c('condition', 'Phase'), na.rm=T)
SRhierAcc$grp <- c('1', '1', '2', '2', '2', '2', '2', '2', '3', '3', '3', '3')
SRhierAcc$condition <- c('aR1', 'aR1', 'aR2', 'aR2', 'aR4', 'aR4', 'F1', 'F1', 'F2', 'F2', 'F4', 'F4')

bb <- ggplot(SRhierAcc, aes(x=condition, y=Acc, group=Phase)) +
  geom_line(aes(color=Phase, group=grp)) +
  geom_point(aes(color=Phase, shape=Phase))+
  coord_cartesian (ylim=c(0,.35)) +
  geom_errorbar(aes(ymin = Acc - se, ymax = Acc + se, color=Phase, width=.5,), size=1.5) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
    panel.background = element_blank(), axis.line = element_line(colour = "black")) +
  ggtitle('Error Rates by Condition') + 
  theme(plot.title = element_text(hjust = 0.5, size=17),
        axis.text.x=element_text(size=15),
        axis.text.y=element_text(size=15), axis.title.x=element_text(size=15),
        axis.title.y=element_text(size=15)) +
  labs(fill=' ', x = ' ', y='Error Rates') +
  scale_x_discrete(labels = c('R1','R2','R4', 'F1', 'F2', 'F4')) + 
  annotate("text", x = 1.4, y = .1, size=4.5, label = "Abstraction Level 0") + 
  annotate("text", x = 3, y = .15, size=4.5, label = "Abstraction Level 1") +
  annotate("text", x= 5.5, y=.33, size=4.5, label = "Abstraction Level 2")

bb
```
Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

